---
title: "Test working"
author: "Muhammad Ilyas"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q2

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q3

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q4

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q5

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q6

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q7

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q8

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q9

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q10

Please include text explanations here (optional) and R code below (optional)

```{r}

```