---
title: "Project Report"
author: "Muhammad Ilyas"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#List the required packages
list.of.packages <- c("ggplot2", "tidyverse", "dplyr", "maptools", "rworldmap", "plotly", "tidyverse", "DT", "png", "countrycode", "ggimage", "corrplot", "treemapify",
"treemap")
#useful function for package loading and installation
#Checks if the package is already installed then skips the installation if not it will be installed
ipak <- function(pkg){
    new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
    if (length(new.pkg)) 
        install.packages(new.pkg, dependencies = TRUE)
    sapply(pkg, require, character.only = TRUE)
}
#load the required packages using the newly created ipak function
ipak(list.of.packages)

#new.packages <- list.of.packages[!(list.of.packages %in% #installed.packages()[,"Package"])]
#if(length(new.packages)) install.packages(new.packages, dependencies = TRUE)

##Install the ggflags from github and load it
#remotes::install_github("ellisp/ggflags", force = T)
library(ggflags)
```

## Q1



```{r}
filenames <- list.files(path = "G:/MSc_Data_Science/MTMH601/MTMH601_Report/MTMH601_Report/trade_database_download", pattern = "*.csv")

# Read in the files
setwd("G:/MSc_Data_Science/MTMH601/MTMH601_Report/MTMH601_Report/trade_database_download")
data <- lapply(filenames, read_csv)
# Combine the data frames
wild <- do.call("rbind", data)

```

## Q2

Now we will look at some visualization

```{r}
wild$ppose <- ifelse(wild$Purpose=="B", "Breeding",

              ifelse( wild$Purpose=="E", "Educational",

                 ifelse ( wild$Purpose=="G", "Garden",

                 ifelse( wild$Purpose=="H", "Hunting",

                 ifelse ( wild$Purpose=="L", "Law",

                ifelse ( wild$Purpose=="M", "Medical",

                 ifelse( wild$Purpose=="R", "reintroduction to wild",

                 ifelse ( wild$Purpose=="P", "Personal",

                 ifelse ( wild$Purpose=="Q", "Circus",

                 ifelse( wild$Purpose=="S", "Scientific",

                 ifelse ( wild$Purpose=="T", "Commercial",

                 ifelse ( wild$Purpose=="Z", "Zoo",

                            "Unknown"))))))))))))




wild$Excountry <- ifelse(wild$Exporter %in% c("CN", "HK"), "China",

                 ifelse( wild$Exporter=="US", "USA",

                 ifelse ( wild$Exporter=="AE", "Unite Arab Emirates",

                 ifelse( wild$Exporter=="BE", "Belgium",

                 ifelse ( wild$Exporter=="CZ", "Czech Republic",

                ifelse ( wild$Exporter=="NL", "Netherlands",

                 ifelse( wild$Exporter=="ID", "Indonesia",

                 ifelse ( wild$Exporter=="IT", "Italy",

                 ifelse ( wild$Exporter=="SG", "Singerpore",

                 ifelse( wild$Exporter=="MY", "Malaysia",

                 ifelse ( wild$Exporter=="JP", "Japan",

                 ifelse ( wild$Exporter=="MG", "Madagascar",

                 ifelse ( wild$Exporter=="FR", "France",

                 ifelse ( wild$Exporter=="DE", "Germany",

                          ifelse ( wild$Exporter=="GB", "Britain",

                 ifelse ( wild$Exporter=="PE", "Peru",

                ifelse ( wild$Exporter=="DE", "Germany",

                          ifelse ( wild$Exporter=="ES", "Spain",

                 ifelse ( wild$Exporter=="ZW", "Zimbabwe",

                  ifelse ( wild$Exporter=="PH", "Philippines",

                 ifelse ( wild$Exporter=="MC", "Monaco",

                           ifelse ( wild$Exporter=="IL", "Israel",

                  ifelse ( wild$Exporter=="AR", "Argentina",

                 ifelse ( wild$Exporter=="GT", "Guatemala",

                           ifelse ( wild$Exporter=="KW", "Kuwait",

                 ifelse ( wild$Exporter=="DK", "Denmark",

                            ifelse ( wild$Exporter=="UY", "Uruguay",

                 ifelse ( wild$Exporter=="GE", "Geogria",

                           ifelse ( wild$Exporter=="PL", "Poland",

                 ifelse ( wild$Exporter=="TN", "Tunisia",

                                 ifelse ( wild$Exporter=="KE", "Kenya",

                 ifelse ( wild$Exporter=="NO", "Norway",

                           ifelse ( wild$Exporter=="UG", "Uganda",

                 ifelse ( wild$Exporter=="MA", "Morocco",

                                   ifelse ( wild$Exporter=="BS", "Bahamas",

                 ifelse ( wild$Exporter=="NP", "Nepal",

                           ifelse ( wild$Exporter=="IN", "India",

                 ifelse ( wild$Exporter=="NI", "Nicaragua",

                                  ifelse ( wild$Exporter=="PY", "Paraguay",

                 ifelse ( wild$Exporter=="AM", "Armenia",

                                   ifelse ( wild$Exporter=="TH", "Thailand",

                 ifelse ( wild$Exporter=="CA", "Canada",

                                  ifelse ( wild$Exporter=="NG", "Nigeria",

                 ifelse ( wild$Exporter=="MX", "Mexico",

                          

                                       ifelse ( wild$Exporter=="CM", "Cameroon",

                 ifelse ( wild$Exporter=="FJ", "Fiji",

                                  ifelse ( wild$Exporter=="ZA", "South Africa",

                 ifelse ( wild$Exporter=="JM", "Jamaica",

                           ifelse ( wild$Exporter=="AD", "Andorra",

                            wild$Exporter)))))))))))))))))))))))))))))))))))))))))))))))))





wild$Imcountry <- ifelse(wild$Importer %in% c("CN", "HK"), "China",

                 ifelse( wild$Importer=="US", "USA",

                 ifelse ( wild$Importer=="AE", "Unite Arab Emirates",

                 ifelse( wild$Importer=="BE", "Belgium",

                 ifelse ( wild$Importer=="CZ", "Czech Republic",

                ifelse ( wild$Importer=="NL", "Netherlands",

                 ifelse( wild$Importer=="ID", "India",

                 ifelse ( wild$Importer=="IT", "Italy",

                 ifelse ( wild$Importer=="SG", "Singerpore",

                 ifelse( wild$Importer=="MY", "Malaysia",

                 ifelse ( wild$Importer=="JP", "Japan",

                 ifelse ( wild$Importer=="MG", "Madagascar",

                 ifelse ( wild$Importer=="FR", "France",

                 ifelse ( wild$Importer=="DE", "Germany",

                          ifelse ( wild$Importer=="GB", "Britain",

                 ifelse ( wild$Importer=="PE", "Peru",

                ifelse ( wild$Importer=="DE", "Germany",

                          ifelse ( wild$Importer=="ES", "Spain",

                 ifelse ( wild$Importer=="ZW", "Zimbabwe",

                  ifelse ( wild$Importer=="PH", "Philippines",

                 ifelse ( wild$Importer=="MC", "Monaco",

                                        ifelse ( wild$Exporter=="IL", "Israel",

                  ifelse ( wild$Importer=="AR", "Argentina",

                 ifelse ( wild$Importer=="GT", "Guatemala",

                           ifelse ( wild$Importer=="KW", "Kuwait",

                 ifelse ( wild$Importer=="DK", "Denmark",

                                           ifelse ( wild$Importer=="UY", "Uruguay",

                 ifelse ( wild$Importer=="GE", "Geogria",

                           ifelse ( wild$Importer=="PL", "Poland",

                 ifelse ( wild$Importer=="TN", "Tunisia",

                                 ifelse ( wild$Importer=="KE", "Kenya",

                 ifelse ( wild$Importer=="NO", "Norway",

                           ifelse ( wild$Importer=="UG", "Uganda",

                 ifelse ( wild$Importer=="MA", "Morocco",

                                   ifelse ( wild$Importer=="BS", "Bahamas",

                 ifelse ( wild$Importer=="NP", "Nepal",

                           ifelse ( wild$Importer=="IN", "India",

                 ifelse ( wild$Importer=="NI", "Nicaragua",

                                  ifelse ( wild$Importer=="PY", "Paraguay",

                 ifelse ( wild$Importer=="AM", "Armenia",

                                   ifelse ( wild$Importer=="TH", "Thailand",

                 ifelse ( wild$Importer=="CA", "Canada",

                                  ifelse ( wild$Importer=="NG", "Nigeria",

                 ifelse ( wild$Importer=="MX", "Mexico",

                          

                                       ifelse ( wild$Importer=="CM", "Cameroon",

                 ifelse ( wild$Importer=="FJ", "Fiji",

                                  ifelse ( wild$Importer=="ZA", "South Africa",

                 ifelse ( wild$Importer=="JM", "Jamaica",

                           ifelse ( wild$Importer=="AD", "Andorra",

                            wild$Importer)))))))))))))))))))))))))))))))))))))))))))))))))

```

## Q3

New file

```{r}

```

## Q4

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q5

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q6

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q7

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q8

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q9

Please include text explanations here (optional) and R code below (optional)

```{r}

```

## Q10

Please include text explanations here (optional) and R code below (optional)

```{r}

```